\documentclass[main]{subfile}
\begin{document}
	
\chapter{1 Major}
		
\section{Intro}

\ifbool{ari}{}
{ % else	
General approach is natural with semi-forcing NT and using \cl2 and \di2 as artificial bids; \cl2 is a GF hand (usually minor oriented or balanced), \di2 is TaJ. 

\section{Response Summary (UPH)}

\begin{bidtable}{1h/\sss}
	\sp1 & Natural, F1 \\
	1NT & Semi-forcing, does not include limit raises.  The only expected invite is balanced. \\
	\cl2 & Art GF.  Most GF hands that have 2-- M will bid this, although \sp1--\he2 is nat GF. \\
	\di2 & TaJ, Limit+ in Opener's major \\
	R & Simple Raise \\
	JS & Jump shifts (including \he1-\sp2) are natural and game invitational \\
	DR & Weak \\
	DJS & Void Splinter; regular splinters start with TaJ \\
	2NT & Mixed Raise \\
	3NT & \rem{T}{Was 17--18 bal, not sure that makes sense in a \cl2 bal world.} Leaving as no agreement for now. \\
\end{bidtable}

\section[2C Art GF]{\cl2 Art GF}

We have removed the 2NT GF response, so \cl2 now acts as a general GF without 3 card support.  No changes to responses, the only minor change is that a 2NT rebid is simply balanced rather than having any inferences about specific minor shapes.

Note that \he2 over \sp1 is still a natural GF.  
 
\begin{bidtable}{1h/\sss,2c}
	\di2 & Waiting, typically denies the other listed hand types \\
	2M & 6+ M \\
	2OM & 4= Nat \\
	2NT & Good 6--4. Weaker 6--4 bids 2M. \\
	3x & 5--5 any strength\\
	3M & Strong suit, setting trumps. Responder shouldn't expect more than 1 side high card control, with 2 honors Opener should likely just open \cl1. \\	
\end{bidtable}

Responder has some structured rebids as well.  Many of these only apply over the \di2 waiting bid.

\begin{bidtable}{1h/\sss,2c,2d}
	2M & Honor doubleton \\
	2OM & Natural, long minor still ambiguous \\
	2NT & Natural balanced.\\
	3m & 6+ \\
	3M & Shortness, 5--5 in the minors (Only over \di2) \\
\end{bidtable}

\begin{bidtable}{1h/\sss,2c,2n}
	\cl3 & Relay for suit LMH \\
	\di3 & 6+ Nat, less interested in other suits. \\
	3M & Hx with slam interest \\
	3OM & 6+ \ccc, as per \di3 \\
\end{bidtable}

\section{TaJ}
	
	1M--\di2 is a limit raise or better and asks for size, with the normal responses being \he2 (min) and \sp2 (max).  2NT kicks off zooming into \"uber responses.  Those are roughly defined as hands which may have slam opposite a perfect Limit Raise.
	
	Over normal responses:
	
	2NT asks TaJ with slam interest.
	
	3M rebids are both "Are you sure?", either good or bad in context.  
	
	New suits are natural length, generally probing for game or possibly a better game.  No one likes to play \sp4 with a 5--5 heart fit.
	
	3NT rebids are choice of games
	 
\section {Other}	

	\ifbool{christian}{
		Over \sp1--\he2, \sp2 is waiting and 2NT is 6+ \sss, other natural. 3m tends to be 5--5.
		
		Direct splinters are voids.  1M--3NT undefined.  Could possibly combine with some two-tiered void splinters potentially.
	}{
	\sp1--\he2 is natural and GF, no special responses.
	} % end else
	
\section{Passed Hand}

Things revert to natural by a PH.  Notably we do not play Drury.  A raise to 2M is our strongest bid, generally constructive.  With a weaker hand we just pass the 1 bid, even with a fit.  (2NT mixed and 3M weak are still both available too.)

Jump shifts are fit.

} %end else
	  
\end{document}


