\documentclass[main]]{subfiles}
\begin{document}

\chapter{Leads}

\section{Opening vs Suits}

We generally lead 3rd/Low from length.  The only real exception is if we have supported partner's suit, we may lead a more attitude type approach. (High from Xxx, low from Hxx, etc.)

Our default honor leads are A from Ace/King. \rem{Mar2022} If we have promised 4+ cards in a suit, we revert to Rusinow honors. Note that transfers such as \di1--(\he1)--Dbl do promise a suit, but negative doubles such as \di1--(\sp1)--Dbl do not promise any one suit, even the other major.  Takeout doubles are presumed to not claim any suit.  Note that if both hands have promised 4+ cards in the suit then either one would lead Rusinow if they are on opening lead.

Signals to honor leads are generally attitude, but if attitude is known they may revert to suit preference.

Example: \di1--(P)--\he1--(Dbl)--\he2 \ldots whichever hand is on lead would lead Rus honors in \hhh. 

\section{Opening vs NT}

Our spot leads are typically 2nd/4th from 4+ cards, top of xxx or fewer. (American 2nd/4th).  As versus suits, we may vary from this in partner's suit. We may lead low from xxx in some situations to show length -- a good example would be after a unsupported weak 2. If dummy is winning the trick and 3rd hand gets to signal, signals are count if the winning card is Q or lower, attitude if K or higher. For this purpose, it is presumed dummy plays the lowest of touching cards.  (e.g., if dummy has KQx and calls ``K'', we would still consider dummy to be winning the Q and is therefore count.)

Honor leads are Rusinow from Q to 9, with 8 being a pivot card\footnote{Pivot card is the break point for Rusinow. 9 promises 10 or shortness, 8 might have the 9 or not.}. ``Shortness'' from a NT Rusinow perspective here is anything less than 4 cards, so we would still lead Q from QJx. We would lead Q from KQx to avoid the power lead, but this is a very rare exception.  

Ace from AK is the default honor lead, with K being the ``power'' lead, asking for count or unblock. (e.g., KQT9). Signals to other honors are generally attitude about the honor below the led card.


\section{Middle of the Hand}

Middle of the hand leads are generally attitude. If we feel that count is important, we will continue to play 3rd/Low vs Suits and 4th vs NT.

Against NT, if we win the opening lead and return the suit, we generally play lowest from 3+ remaining and high from 2. It is also possible that a high card might be led to hold the lead which may be done with any number.

Honors revert to standard. 

\chapter{Signal agreements}

General carding rules: upside down count and attitude, regular suit preference. Priority of signals when partner on lead is Attitude/Suit Preference/Count; priority for following suit is Suit Pref/Count. When count is ``necessary'' we give count signals, but in general most cards following suit are S/P or just following suit.

For a more specific example from play, see 

Discards are generally attitude based.

\section{Suit Preference}  

Standard S/P means high for high and low for low.  Often times this is sufficient when a suit can be eliminated (such as trumps.) Middle cards are sometimes used to encourage the suit led despite a normal S/P situation (singleton on the board) or to encourage a trump shift.

Other suit preference situations, such as following suit, there are often 3 suits in play. Sometimes we can infer a suit not being reasonable, but otherwise we encode in the following manner:

With 2 cards to signal: High-Low indicates a high or middle suit, Low-High indicates a low suit or no preference.

With 3 cards to signal:

\begin{description}
	\item [LMH:] Neutral or Mild Low suit
	\item [LHM:] Strong low suit
	\item [MHL:] Mild Middle
	\item [MLH:] Strong Middle
	\item [HLM:] Mild High
	\item [HML:] Strong High
\end{description}

The unifying concept here is we always start with the suit we want to make (LMH). Then the more ``active'' we are (using higher spots) the more we like the suit we signaled.  For example, Middle then Low shows that we were actively signaling, so if we don't get a chance to complete the high at least partner will know we are interested in something. If we started MH they may not know this wasn't LH from 2.

\chapter{Examples from Play}

\section{Lost in Translation}

Often times, it is important to signal with the clearest card possible. While subtleties can be nice, there is a danger that partner will not pick up on the message. 

NABC+ BAM, SF 2019. 1st Qual. (rotated)

\begin{handdiagram}
	\north{76,akq,j53,qj986}
	\south{q94,762,t84,ak54}
	\east[Ari]{t83,954,aq72,t72}
	\west[Tom]{akj52,jt83,k96,3}
\end{handdiagram}	 	

\auction[Tom,,Ari,]{,,,p,1s,x,2s,3c,3s,4c}

\spades{K} lead, 6, \textit{8}, 4.

\spades{A}, 7, 3, 9.

\hearts{3} \ldots

Ari was attempting to be subtle to try to show a diamond s/p. Tom thought at trick 1 that the 8 might be low (since the QT9 were still out). Once it was proven at trick 2 to not be the case, Tom put Ari on Q83, since from T83 he could play the T at trick 1. This led Tom to thinking that there was no need to switch to diamonds as there was no discard in spades. We dropped 1 trick. The board was still won at +100, but should have been +200.

Tom thinks the best sequence is the T at trick 1, then the 4 for low s/p. 

\section{Average hand}

NABC+ BAM, SF 2019.  1st Qual (rotated)

\begin{handdiagram}
	\north{q73,j8,aq98654,q}
	\south{k9,aq,,at9876432}
	\east[Tom]{at54,t42,kt72,kj}
	\west[Ari]{j862,k97653,j3,5}
\end{handdiagram}	

\auction[Ari,,Tom,]{,,,1c,2h,3d,3h,3n}

\hearts {6}, 8, T, Q

\clubs {A}, 5, Q, J

\clubs {T}, \hearts {3}, \diamonds {4}, \clubs {K}

\spades {4} \ldots

Declarer made a creative 3NT bid. Their play at trick 2 was surprising. Tom played the \clubs {J} in a hope to indicate a holding like this. Declarer's \clubs{T} was a mistake, they should lead a lower spot. The 10 was much  too revealing, showing the 9 card suit to the defense. Ari didn't process this and discarded a heart in the hopes that it would indicate that he didn't have a spade card. Tom was desperate for a spade signal, as he knew declarer had \exactshape{2209} with the \hearts {AQ}. The only question was whether declarer had the \spades {K} or not. If no, a low spade back might beat the hand if Ari has both honors and break even otherwise. If yes, Tom must play a heart to wait for the \spades {A} and a heart trick at trick 12. Tom interpreted the heart as encouraging due to an entry (in spades) and therefore played a low spade.

A direct signal in spades would have been more useful, the levels of indirection were ambiguous.

The result didn't matter, teammates were in \cl6 down 1, so making 4 or 6 were both a loss.

\end{document}