\documentclass[main]{subfile}
\begin{document}

\chapter{Introduction by Tom}

Since I needed to rebuild the document structure anyway, I'm taking this opportunity to merge the document flow for the Jenni, Ari and Christian partnerships into a single new grand unification of the notes.  

\LaTeX ~Technical comment:  the main meat of the document will be maintained to be compatible with all partnerships, the document will be compiled with the appropriate name-tom.tex file to generate that PDF.  The notes will be interspersed with \textit{ifbool} statements to ensure the accuracy for the individual partnership while allowing the common elements to only need a single point of editing to ensure consistency across.

\section{Versions}

\ifbool{christian}{
\subsection{23.3.9}

\begin{itemize}
	\item Updated To Do
	\begin{itemize}
		\item xfers/\cl2 confirmed and in notes
		\item Remove \second ~\& ~\fourth carding
		\item xfer McCabe moved to notes
		\item \di1--1NT--2M for inv/GF unbal hands.
	\end{itemize}
	\item System Summary
	\begin{itemize}
		\item Remove reference to old \di2 opener
		\item Relay, text clean up for +6 step
	\end{itemize}
	\item \cl1--\di1
	\begin{itemize}
		\item Text clean up 
		\item Adding "subsection" structure for clarity
		\item Adding inv+ xfer/xfer to 1NT rebid
		\item Expanding Kokish agreements over \he3 rebid
	\end{itemize}
	\item \di1--2M updates
	\item 1NT 2nd xfer sequences now Inv+ when Responder is limited.  (PH or \cl1--\di1--1NT) Rebids are natural over these.
\end{itemize}
}{}
\subsection{Initial Version - 22.11.0}

Canonical version, will include any changes from previous March 2022 version of tom-jenni.  Ari version hasn't been touched in a bit so I will try to pull in the notes ``as is''.

\section{Notation}

Notation hasn't changed from previous versions, with one new addition:  just as we use "5+ \textit{suit}" to indicate 5 or more cards in a suit, I'm introducing "5= \textit{suit}" to mean exactly 5 cards, no more no less.  Similarly "5- \textit{suit}" means 5 or fewer cards.

% previous version used a description environment instead

\begin{destable}
	R & Simple Raise \\
	R+1 & One above a simple raise \\
	DR & Double Raise \\
	TR & Triple Raise \\
	LMH &  Low-Middle-High\\
	LHB & Low-High-Both (Shortness relay after 10+ known cards.) \\
	+1& Next Bidding Step \\
	M& Major.  If one has been shown, it is the same one. \\
	OM& Other Major.  After a major is shown.\\
	m,om& Minor, other minor.\\
	JS& Jump Shift\\
	DJS& Double Jump Shift\\
	UTL& Up The Line (\ccc\ddd\hhh\sss)\\
	COG& Choice of Games\\
	OKC& Optional Key Card\\
	\#+suit& \# or more cards in the suit\\
	\#--suit& \# or fewer cards in the suit\\
	\#=suit& exactly \# cards in the suit\\
\end{destable}


\end{document}