\documentclass[main]{subfile}
\begin{document}
\chapter{Slam Bidding}

\section{RKC}

In general, we play a 1430 style of RKC with ``Redwood'':  +1 RKC for minors, 4NT RKC for majors.

Over the Q ask, we play new suits as showing both the Q and the lowest ranking side K.  5NT when there is room to show all the Ks in undefined, although Ari bid it at the table intending it as 2 side Ks.  To Tom, 5NT is a substitute for a K when needed but unclear what the meaning is/should be otherwise.

\subsection{Exclusion}
\ifbool{christian}{Exclusion is 1430 if the asking bid is below the 5 level, or 0314 if on the 5 level.}{Exclusion is always 0314, the only non-1430 RKC we play.}

\subsection{Preempt KC}

Auctions such as weak 2 - \cl4, responses are fairly typical:  0, 1 w/o Q, 1 w/, 2.  Note we won't have 2 with so no steps beyond this are required.

\subsection{Showing Voids}

I do not believe we have any firm agreements as to how to show a void over 4NT RKC.  There are a number of schemes, none of which are all that great.  Open to suggestions.

\subsection{Possible Improvements}

I may want to explore using a spiral style of Response to Q-Ask rather than Specific King.  Something like a stop/go scheme (like SQUARE):

\begin{longtblr}[entry=none,label=none]{colspec=lp{.6\textwidth},width=.75\textwidth}
	+1 & No Q \\
	+2 & Q but no low K \\
	+3 & Q and low K but not medium K \\
\end{longtblr}

\ldots and so on.

\section{Cuebid Style}

Most cuebids are loose as to \first control strictly vs. \first/~\second.  In situations where a very strong hand is cuebidding it is generally assumed to be first, whereas a weaker hand cuebidding can be anything.

\section{Other}

3NT is Non-Serious in many auctions, over which all cuebids are \first/~\second style.  Note that we never use other bids for Non-S, only 3NT.

\end{document}