\documentclass[main]{subfile}

\begin{document}
	
\chapter{Weak 2 bids}
\ifbool{christian}
{ 
We play weak 2 bids in \ddd ~and \sss. Our bids are mostly undisciplined.  Non-vul 5 card suits are common, vul they are unexpected. (A 7 card suit is possible instead.) The HCP range is nominally 3--9, but it should be noted that 9 with 6= is often a 1 bid in our style.

+1 is 5/7 Ogust.  (\di2--\he2 or \sp2--2NT).  \di2--2NT is the forcing heart response.  \rem{T}{As of the current writing I believe \di2--\sp2 is forcing but there was discussion about changing that.}

\begin{bidtable}{2d/\sss,+1}
	+1 & An odd number of trumps, 5 NV or 7 Vul. Next step asks strength bad/medium/good \\
	+2 & 6, bad opener \\
	+3 & 6, medium opener \\
	+4 & 6, good opener \\
	 & \pgfornament[color=tomdark, scale=.15, anchor=south]{17}\pgfornament[color=tomdark, scale=.15, anchor=south]{17}\pgfornament[color=tomdark, scale=.15, anchor=south]{17}\textbf{\di2 Only}\pgfornament[color=tomdark, scale=.15, anchor=south]{18}\pgfornament[color=tomdark, scale=.15, anchor=south]{18}\pgfornament[color=tomdark, scale=.15, anchor=south]{18}\\
	\he3 & 4= \sss, 6 \ddd \\
	\sp3 & 4= \hhh, 6 \ddd \\
	3NT & 4= \ccc, 6 \ddd \\
\end{bidtable}  

}
{ %else
Weak 2s, fairly undisciplined. Non-vul 5 card suits are common, vul they are unexpected. (7 card suit possible.) The range is 3--9 HCP. Note that many 9s with 6 card suits are opened on the 1 level.

New suits are natural and forcing. 2NT is a modified Ogust system I've named ``5/7 Ogust''.

	\begin{bidtable}{\orauction{2M,2NT}}
		\cl3 & An odd number of trumps, 5 NV or 7 Vul. \di3 asks strength as per below. \\
		\di3 & 6, bad opener \\
		\he3 & 6, medium opener \\
		\sp3 & 6, good opener \\
		3NT & 6, 4 in other major. Good enough to commit to game. \\
	\end{bidtable}
		
Preempt RKC:

	\begin{bidtable}{\orauction{2M,4c}}
		\di4 & 0 KC \\
		\he4 & 1 KC, no trump Q \\
		\sp4 & 1 KC, trump Q \\
		4NT & 2 KC, no trump Q \\
		\cl5 & 2 with Q in theory, unlikely response \\
	\end{bidtable}
} % end else	
\end{document}



